A Case Study in Preserving a High Energy Physics Application

### 2014-01-20 paper.tex
add pics

\section{Introduction of the exmaple}
\subsection{Background}
Matthias, one graduate student from Physics Department of University of Notre Dame, finished one interesting tau analysis. We want to understand how the tau analysis works and repeat it.

@@

@@

\section{Solution 3 to Repeat the Program}
The overview of the architecture is shown in ~\ref{fig:Overview of architecture}.

@@

@@

\subsection{Discussion of Solution 3}
Under Solution 3, the reproduction of one analysis program becomes easier.The namespace of repeating one experiment will be limited into one independent package containing all the data and software dependencies of one analysis program.

Rethink Matthias's example, under Solution 3, the reproduction of it only needs the necessary environment variables, svn login,  the actual analysis command and the package. If different scholars want to repeat one analysis program, what they need to do is to obtain the package and rerun the actual analysis program. Under Solution 2, each scholar needs to get the necessary data and software, and then prepare software environment.

@@

The architecture of preservation integration of multiple programs is shown in ~\ref{fig:Preservation intergration}.

@@

>>>>

\section{Introduction of the exmaple}

Matthias, one graduate student from Physics Department of University of Notre
Dame, finished one interesting tau analysis. Others want to understand how the tau
analysis works and repeat it.

\subsection{Background}

@@

\begin{figure}
\centering
\epsfig{file=data-process.eps, height=3in, width=3in}
\caption{Data Process}
\label{fig:data-process}
\end{figure}

The data process is shown in Figure~\ref{fig:data-process}.

@@

\section{Solution 3 to Repeat the Program}
\subsection{Dependencies of the Program}

Figure~\ref{fig:Overview of architecture} illustrates all the dependencies involved in the program, which can be divided into two categories: clear dependencies and implicit dependencies. Clear dependencies include data dependencies and direct software dependencies which can be extracted directly from the analysis program. Implicit dependencies include indirect software dependencies which is necessary for the successful execution of direct software dependencies and other implicit dependencies. For example, we know Git is one direct software dependency from the analysis program, which further depends on perl, python, rsync, openssh-clients and other packages. The analysis program accesses one file File1, which is one soft link file further referring to File2.

Implication: One mechanism which can mine all the dependencies of the program is necessary.

@@

\begin{figure}
\centering
\epsfig{file=solution3.eps, height=3in, width=3in}
\caption{Relationship of Roles}
\label{fig:solution3}
\end{figure}

The relationship of different roles involved experiment preservation and reproduction is shown in Figure~\ref{fig:solution3}.
The original author is responsible for generating one package based on the successful execution sandbox with the help of the packaging utility. Then the package, together with the map file and description file will be uploaded into the archive. When another scholar wants to repeat the experiment, one copy of the package and its corresponding map file will be downloaded into the new machine.

\subsection{Structure of Map File}

The map file of one package supports pattern matching semantics,
which greatly reduces the scale of the map file and improves the efficiency of file path redirection. 
For example,
one item inside the map file is "/dir1 /package-dir1" means that the access to each file and
subdirectory under /dir1 will be redirected into /package-dir1.
If the semantics of the map file do not support pattern matching, the size of the map file will become astonishing. 
/dir1 may contain thousands of files, which will generates thousands of map items and will take more time to redirect file paths.

In the map relationship shown above, During the packaging process, we noticed
that it is impossible to copy the files under certain directories like /dev.
For example, during namelist acquisition process, three special files under /dev directory were recorded into the namelist: tty, null and urandom, which are used for input and output.
We tried to copy these files into the new package, but the packaging utility halted.
We also noticed that copying the files under directories like /proc is
meaningless. Because the process id of one program is random and depends on the
current allocation of process ID. As for these two file categories, letting
the program directly utilize the files on the machine, where the new user
repeats the program, is a better choice. The semantics is implemented by
setting the target path of one file equal to the origin file path inside the
map file. For example, "/dev /dev" means that when the program needs to access
files under /dev directory, it will directly use the file under /dev, which is
independent from the namespace of the package. This semantics also makes the
reference of files outside the package possible. If the new user wants to
expand the analysis of one program to his own data with the path of /A, he can add the analysis
code into the analysis script and add one item "/A /A" into the map file.

@@

\subsection{Discussion of Solution 3}

Under Solution 3, the reproduction of one analysis program becomes easier.
Rethink Matthias's example, the reproduction of it only needs
the necessary environment variables, svn login, the actual analysis command
and the package. If different scholars want to repeat one analysis program,
what they need to do is to obtain the package and rerun the actual analysis
program. Under Solution 2, each scholar needs to get the necessary data and
software, and then prepare software environment.

%here is the new content-hmeng
The starting point of Solution 3 is one successful execution sandbox on the original machine. 
Parrot traps all the system calls and copies each accessed file (except for common dependencies) into one new package.
The necessary scientific data will be copied into the target package.
The software dependencies can be divided into two categories: clear dependencies, which can be observed directly through reading the analysis script and implicit dependencies,
which can not be obtained through reading the analysis script. 
Parrot can obtain every dependency through trapping each system call.
Strictly speaking, the software concept and the scientific data concept are lost in Solution 3, because
the granularity of parrot is file.
The same thing happens to network resources.
Packaging utlity maintains one list of common dependencies and first judges whether the file belongs to this list before trying to copy one file into the package.
As for the computing environment, Solution 3 notices the new user through the description information at the beginning of the script.
%the following subsection belongs to the "discussion of data and software
%preservation" section

@@

The architecture of preservation integration of multiple programs is shown in ~\ref{fig:Preservation integration}. Script 1 and Script 2, sharing one same dependency B, belongs two different programs. Without preservation integration, B will be preserved twice in the archive, which is space-consuming. To improve the utilization efficiency of storage resources, preservation integration of multiple programs is necessary. In the archive, only one copy of B is stored, which is referred by both scripts 1 and script 2.

@@

\subsection{Preservation of Large Data}

The preservation policy must concern about the size of data. If its size is
small, copying it into one pacakge and transferring it between different
machines is not a bad idea.Howerver, when the size becomes large, copying it
into one package will make the size of the package uncontrollable.  In
Figure~\ref{fig:Preservation integration}, the size of C is very large and
easily to be obtained through Internet by different users. Directly referring C
as network resources is more efficient than preserving it into one package.

\subsection{Mining of Dependencies}

The mining degree of data and software dependencies greatly determines the
repeatability of one experiment. Data dependencies is easy to figured out.
However, the situation of software dependencies is complex. The software
dependencies include OS, hardware platform, software directly forked inside the
progam and software indirectly forked by directly forked software. The first
three categories are easy to deal with. The description of indirect software
dependencies needs more efforts. One solution is to utlize package management
tools, like rpm, pacman, apt, to recursively trace each direct software
dependency and generate one clear dependency graph. With the dependency graph,
the new user can configure the software environment and repeat the experiment.
Solution 3 odopts this solution, which is easy to implement, but leaves the
complex environment configuration to the new users.

Another solution is to treat the computing environment, software environment
and scientific data as one integral entirety and preserve the entirety
completely. The reproduction of one experiment using this solution is easier.
However, the original machine is not only for one special experiment and may
concern a large amount of software and data unrelevant to the experiment. The
time and space overhead of this solution must be considered.

%\subsection{The preservation} When the authors and the programs becomes more
%and more, the whole pool of one repo may be nearly to be preserved. why not
%directly copy the whole repo and preserve it at the begining directly?  Answer:
%we must concern the efficiency of repeating one small and simple program.
\subsection{Preservation Degree of Directory Structure}

Data and software preservation of physics experiments must concern the
preservation degree of the original filesystem.  The three core components of
one filesytem are file, directory and metadata.  The access of files can be
divided into two categories: only access file metadata, like size, ownership,
access authority list, and access both the file content and metadata.  If both
the content and metadata need to be accessed, the whole file must be copies
into the package.  However, if only the metadata of one file is accessed, how
to preserve the file needs to be considered carefully. If the size of the file
is 1KB or 1MB, preserving the content is acceptable. If the size of one file is
1GB, preserving the whole file just for the access of its metadata is
inefficient.

Directory is one list of files and subdirectories under it. At first, we only
copied the accessed items under one directory and ignored the unaccessed items.
However, some operations on one directory depends on each item under it. For
example, `ls /dirA` is one linux command to list the name of each item under
/dirA. Because the directory itself has the name list of items under it, only
the path of the directory was recorded into the namelist in the first phrase of
Solution 3. However, when we repeated the command `ls /dirA` using the
preserved package, it returned NULL because none of items under it existed in
the package. If one routine within the original program depends on the return
value of `ls /dirA`, the behavior of the whole program will become incorrect
and unpredictable. Lessons: all the items under one directory must be copied
into the package to ensure the semantics of the original program. However, the
time and space overhead appears again. Currently, Solution 3 creates one item
with the same name but the size of zero for each item under /dirA. Another
solution is to introduce one database to preserve the metadata of each file and
directory and record the origial metadata into the database.

\subsection{Here is the Useful Package}

At the beginnig of our case study, we generated one package for Matthias's
example based on Solution 3. Several months later, the original machine meets
some problems and the access model of CMSSW was also modified. In this case, if
you want to repeat Matthias's example on the original machine, different 
configurations, including CMSSW\_ARCH, environment variables and CVS access
authority need to be modified. However, with the generated package and map file, we can repeat the experiment directly on the same machine.
%here is the new content-hmeng
